---
title: "Resources Catalog"
subtitle: "A curated collection of data science resources for R, Python, and beyond."
description: "A curated and filterable catalog of 1,000+ data science resources for R, Python, and beyond."
search: false
format:
  html:
    toc: false
    page-layout: full
    css: ../assets/stylesheets/resources-catalog.css
execute:
  echo: false
---

```{r resource-catalog-setup}
#| message: false
#| warning: false

library(dplyr)
library(htmltools)
library(purrr)
library(stringr)
library(yaml)

source(here::here("_helpers", "resources_catalog.R"))

resources <- load_resources_catalog(here::here("data", "resources.txt"))

n_total <- nrow(resources)
all_types <- sort(unique(resources$type))
cards <- map(seq_len(n_total), function(index) {
  make_resource_card(resources[index, ], index)
})
```

```{r resource-catalog-controls}
# ── Build controls HTML ───────────────────────────────────────────────────────

# Language filter chips
lang_chip_defs <- list(
  list(value = "r",      label = "R",      color = "color: #1a579d; border-color: rgba(26,87,157,0.4);"),
  list(value = "python", label = "Python", color = "color: #3a7a20; border-color: rgba(55,125,34,0.4);"),
  list(value = "julia",  label = "Julia",  color = "color: #8b33b3; border-color: rgba(149,57,191,0.4);"),
  list(value = "other",  label = "Other",  color = "color: #555f6a; border-color: rgba(108,117,125,0.35);")
)

# Super-category filter chips
super_chip_defs <- list(
  list(value = "machine learning & ai", label = "ML & AI"),
  list(value = "statistics",            label = "Statistics"),
  list(value = "r & shiny",             label = "R & Shiny"),
  list(value = "data visualization",    label = "Viz"),
  list(value = "python & devops",       label = "Python & DevOps"),
  list(value = "education",             label = "Education"),
  list(value = "community & events",    label = "Community"),
  list(value = "life sciences",         label = "Life Sciences"),
  list(value = "research",              label = "Research"),
  list(value = "general",              label = "General")
)

make_chip <- function(value, label, extra_style = NULL) {
  attrs <- list(
    class = "btn filter-chip",
    `data-filter-group` = if (value %in% map_chr(lang_chip_defs, "value")) "language" else "super",
    `data-filter-value` = value,
    `aria-pressed` = "false"
  )
  if (!is.null(extra_style)) attrs$style <- extra_style
  do.call(tags$button, c(attrs, list(label)))
}

lang_chips_html <- map(lang_chip_defs, function(d) {
  make_chip(d$value, d$label, d$color)
})

super_chips_html <- map(super_chip_defs, function(d) {
  attrs <- list(
    class = "btn filter-chip",
    `data-filter-group` = "super",
    `data-filter-value` = d$value,
    `aria-pressed` = "false"
  )
  do.call(tags$button, c(attrs, list(d$label)))
})

type_options <- c(
  list(tags$option(value = "", "All types")),
  map(all_types, function(t) tags$option(value = tolower(t), t))
)

tagList(
  tags$div(
    class = "controls-wrapper",
    # Row 1: search + view toggle
    tags$div(
      class = "controls-search-row",
      tags$div(
        class = "resource-search-wrap input-group",
        tags$span(
          class = "input-group-text",
          tags$i(class = "bi bi-search")
        ),
        tags$input(
          type = "text",
          id = "resource-search",
          class = "form-control",
          placeholder = paste0("Search ", n_total, " resources by title, category, or URL\u2026"),
          `aria-label` = "Search resources"
        )
      ),
      # View toggle
      tags$div(
        class = "d-flex gap-1 flex-shrink-0",
        tags$input(
          type = "radio",
          class = "btn-check",
          name = "view-toggle",
          id = "grid-view-btn",
          checked = NA
        ),
        tags$label(
          class = "view-toggle-label",
          `for` = "grid-view-btn",
          tags$i(class = "bi bi-grid-3x3-gap me-1"),
          "Grid"
        ),
        tags$input(
          type = "radio",
          class = "btn-check",
          name = "view-toggle",
          id = "list-view-btn"
        ),
        tags$label(
          class = "view-toggle-label",
          `for` = "list-view-btn",
          tags$i(class = "bi bi-list-ul me-1"),
          "List"
        )
      )
    ),
    # Row 2: language chips
    tags$div(
      class = "controls-chips-row",
      tags$span(class = "filter-section-label", "Language"),
      tags$div(class = "filter-divider"),
      lang_chips_html
    ),
    # Row 3: super-category chips
    tags$div(
      class = "controls-chips-row",
      tags$span(class = "filter-section-label", "Topic"),
      tags$div(class = "filter-divider"),
      super_chips_html
    ),
    # Row 4: type dropdown + sort + clear + counter
    tags$div(
      class = "controls-bottom-row",
      do.call(tags$select, c(list(id = "type-filter"), type_options)),
      tags$select(
        id = "sort-select",
        tags$option(value = "default", "Sort: A \u2192 Z"),
        tags$option(value = "date-desc", "Sort: Date \u2193 (newest)"),
        tags$option(value = "date-asc",  "Sort: Date \u2191 (oldest)")
      ),
      tags$button(
        id = "clear-filters",
        class = "btn btn-sm",
        style = "font-size: 0.78rem; border: 1.5px solid var(--bs-border-color, rgba(128,128,128,0.25)); border-radius: 0.375rem; padding: 0.25rem 0.65rem;",
        tags$i(class = "bi bi-x-circle me-1"),
        "Clear"
      ),
      tags$div(
        class = "catalog-counter",
        "Showing ",
        tags$strong(id = "resources-count", as.character(n_total)),
        " of ",
        tags$strong(as.character(n_total)),
        " resources"
      )
    )
  )
)
```

```{r resource-catalog-cards}
# ── Results view ───────────────────────────────────────────────────────────────
tagList(
  tags$div(
    id = "resource-catalog",
    class = "catalog-view catalog-view-grid",
    tags$div(
      id = "catalog-results",
      class = "catalog-results",
      cards
    ),
    tags$div(
      id = "no-results-msg",
      tags$i(class = "bi bi-search me-2"),
      "No resources match your current filters.",
      tags$button(
        id = "no-results-clear",
        class = "btn btn-link btn-sm p-0 ms-2",
        style = "font-size: inherit;",
        "Clear filters"
      )
    )
  ),
  tags$div(id = "catalog-pagination")
)
```

```{=html}
<script src="../assets/scripts/resources-catalog.js"></script>
```

::: {.callout-note}
## Contributing
Want to add a resource? Edit `data/resources.txt` and open a PR on [GitHub](https://github.com/antoinelucasfra/antoinelucasfra.github.io). Each resource is a small YAML block:

```yaml
---
title: "Resource Title"
type: Book
link: https://example.com
language: R
category: "Statistics;Tutorial"
description: "A brief one-sentence description shown on hover and in search."
---
```

The `description` field is optional but recommended — it powers the hover tooltip on each card title and is included in the full-text search.

See [CONTRIBUTING.md](https://github.com/antoinelucasfra/antoinelucasfra.github.io/blob/main/CONTRIBUTING.md) for the full guide, including the automated workflow for adding resources via Google Keep.
:::

*Links to external websites are provided for convenience and informational purposes only.*
