---
title: "Resources Catalog"
subtitle: "A curated collection of data science resources for R, Python, and beyond."
format:
  html:
    toc: false
    page-layout: full
execute:
  echo: false
  freeze: false
---

```{css, echo=FALSE}
/* ── Quick filter chips ──────────────────────────────────────────────────── */
.filter-chip {
  border-radius: 999px;
  font-size: 0.78rem;
  font-weight: 500;
  padding: 0.25rem 0.75rem;
  transition: all 0.15s ease;
  white-space: nowrap;
  border: 1.5px solid currentColor;
  background: transparent;
  cursor: pointer;
}

.filter-chip:focus {
  box-shadow: 0 0 0 3px rgba(56, 189, 248, 0.3);
  outline: none;
}

.filter-chip.active {
  background-color: #0F1117 !important;
  border-color: #38BDF8 !important;
  color: #38BDF8 !important;
}

[data-bs-theme="dark"] .filter-chip.active {
  background-color: #38BDF8 !important;
  border-color: #38BDF8 !important;
  color: #0F1117 !important;
}

/* ── Controls bar ────────────────────────────────────────────────────────── */
.controls-wrapper {
  background-color: var(--bs-body-bg);
  border-radius: 0.5rem;
  border: 1px solid var(--bs-border-color, rgba(128, 128, 128, 0.2));
  padding: 1rem;
  margin-bottom: 1.25rem;
}

.controls-search-row {
  display: flex;
  gap: 0.75rem;
  align-items: center;
  margin-bottom: 0.75rem;
  flex-wrap: wrap;
}

.controls-chips-row {
  display: flex;
  flex-wrap: wrap;
  gap: 0.4rem;
  align-items: center;
  margin-bottom: 0.6rem;
}

.controls-bottom-row {
  display: flex;
  gap: 0.75rem;
  align-items: center;
  flex-wrap: wrap;
}

.filter-section-label {
  font-size: 0.68rem;
  font-weight: 700;
  letter-spacing: 0.07em;
  text-transform: uppercase;
  color: var(--bs-secondary-color, #6c757d);
  align-self: center;
  white-space: nowrap;
}

.filter-divider {
  width: 1px;
  height: 1.4rem;
  background-color: var(--bs-border-color, rgba(128, 128, 128, 0.25));
  align-self: center;
  flex-shrink: 0;
}

/* ── Search input ────────────────────────────────────────────────────────── */
.resource-search-wrap {
  flex: 1 1 280px;
  min-width: 200px;
}

.resource-search-wrap .input-group-text {
  background-color: var(--bs-body-bg);
  border-color: var(--bs-border-color, rgba(128, 128, 128, 0.25));
  color: var(--bs-secondary-color);
}

.resource-search-wrap input[type="text"] {
  background-color: var(--bs-body-bg);
  border-color: var(--bs-border-color, rgba(128, 128, 128, 0.25));
  color: var(--bs-body-color);
  font-size: 0.85rem;
}

.resource-search-wrap input[type="text"]:focus {
  border-color: #38BDF8;
  box-shadow: 0 0 0 3px rgba(56, 189, 248, 0.2);
}

/* ── Type select ─────────────────────────────────────────────────────────── */
#type-filter {
  background-color: var(--bs-body-bg);
  border: 1.5px solid var(--bs-border-color, rgba(128, 128, 128, 0.25));
  border-radius: 0.375rem;
  color: var(--bs-body-color);
  font-size: 0.78rem;
  font-weight: 500;
  padding: 0.25rem 1.8rem 0.25rem 0.75rem;
  max-width: 180px;
  cursor: pointer;
}

#type-filter:focus {
  border-color: #38BDF8;
  box-shadow: 0 0 0 3px rgba(56, 189, 248, 0.2);
  outline: none;
}

/* ── View toggle ─────────────────────────────────────────────────────────── */
.view-toggle-label {
  cursor: pointer;
  border-radius: 0.375rem;
  padding: 0.25rem 0.6rem;
  font-size: 0.78rem;
  color: var(--bs-body-color);
  border: 1.5px solid var(--bs-border-color, rgba(128, 128, 128, 0.25));
  transition: all 0.15s ease;
  user-select: none;
}

.btn-check:checked + .view-toggle-label {
  background-color: #0F1117;
  border-color: #38BDF8;
  color: #38BDF8;
}

[data-bs-theme="dark"] .btn-check:checked + .view-toggle-label {
  background-color: #38BDF8;
  border-color: #38BDF8;
  color: #0F1117;
}

/* ── Counter ─────────────────────────────────────────────────────────────── */
.catalog-counter {
  font-size: 0.8rem;
  color: var(--bs-secondary-color, #6c757d);
  margin-left: auto;
  white-space: nowrap;
}

.catalog-counter strong {
  color: var(--bs-body-color);
}

/* ── Resource cards ──────────────────────────────────────────────────────── */
.resource-card {
  border: 1px solid var(--bs-border-color, rgba(128, 128, 128, 0.2));
  border-radius: 0.5rem;
  transition: border-color 0.15s ease, box-shadow 0.15s ease;
  background-color: var(--bs-body-bg);
}

.resource-card:hover {
  border-color: #38BDF8;
  box-shadow: 0 2px 10px rgba(56, 189, 248, 0.15);
}

.resource-card .card-body {
  padding: 0.85rem;
}

.resource-title a {
  color: var(--bs-body-color) !important;
  text-decoration: none;
  font-weight: 600;
  font-size: 0.88rem;
  line-height: 1.35;
}

.resource-title a:hover {
  color: #0F1117 !important;
  text-decoration: underline;
}

[data-bs-theme="dark"] .resource-title a:hover {
  color: #38BDF8 !important;
}

/* ── Resource list items ─────────────────────────────────────────────────── */
.resource-item {
  background-color: var(--bs-body-bg);
  border-color: var(--bs-border-color, rgba(128, 128, 128, 0.2)) !important;
  transition: background-color 0.12s ease;
  padding: 0.6rem 0.85rem !important;
}

.resource-item:hover {
  background-color: rgba(56, 189, 248, 0.06) !important;
}

.resource-item .resource-title a {
  font-size: 0.87rem;
}

/* ── Resource type badges ────────────────────────────────────────────────── */
.resource-type {
  font-size: 0.65rem;
  font-weight: 700;
  letter-spacing: 0.05em;
  text-transform: uppercase;
  border-radius: 0.25rem;
  padding: 0.2em 0.55em;
  flex-shrink: 0;
}

/* ── Language & category chips ───────────────────────────────────────────── */
.chip {
  display: inline-block;
  padding: 0.1rem 0.42rem;
  font-size: 0.66rem;
  font-weight: 500;
  border-radius: 999px;
  margin: 0.08rem 0.1rem 0.08rem 0;
  white-space: nowrap;
  line-height: 1.5;
}

.chip-r {
  background-color: rgba(26, 87, 157, 0.13);
  color: #1a579d;
  border: 1px solid rgba(26, 87, 157, 0.22);
}

.chip-python {
  background-color: rgba(55, 125, 34, 0.13);
  color: #3a7a20;
  border: 1px solid rgba(55, 125, 34, 0.22);
}

.chip-julia {
  background-color: rgba(149, 57, 191, 0.13);
  color: #8b33b3;
  border: 1px solid rgba(149, 57, 191, 0.22);
}

.chip-other {
  background-color: rgba(108, 117, 125, 0.1);
  color: #555f6a;
  border: 1px solid rgba(108, 117, 125, 0.18);
}

.chip-cat {
  background-color: rgba(26, 42, 74, 0.07);
  color: var(--bs-body-color);
  border: 1px solid rgba(26, 42, 74, 0.14);
}

[data-bs-theme="dark"] .chip-r {
  background-color: rgba(26, 87, 157, 0.28);
  color: #7ab8f5;
  border-color: rgba(26, 87, 157, 0.4);
}

[data-bs-theme="dark"] .chip-python {
  background-color: rgba(55, 125, 34, 0.28);
  color: #90d070;
  border-color: rgba(55, 125, 34, 0.4);
}

[data-bs-theme="dark"] .chip-julia {
  background-color: rgba(149, 57, 191, 0.28);
  color: #d49bf5;
  border-color: rgba(149, 57, 191, 0.4);
}

[data-bs-theme="dark"] .chip-other {
  background-color: rgba(108, 117, 125, 0.2);
  color: #adb5bd;
  border-color: rgba(108, 117, 125, 0.3);
}

[data-bs-theme="dark"] .chip-cat {
  background-color: rgba(56, 189, 248, 0.08);
  color: #7DD3FC;
  border-color: rgba(56, 189, 248, 0.2);
}

/* ── Category expand toggle ──────────────────────────────────────────────── */
.category-expand-toggle {
  font-size: 0.66rem;
  font-weight: 600;
  color: var(--bs-secondary-color, #6c757d);
  background: transparent;
  border: 1px solid var(--bs-border-color, rgba(128, 128, 128, 0.2));
  border-radius: 999px;
  padding: 0.08rem 0.38rem;
  cursor: pointer;
  line-height: 1.5;
  vertical-align: middle;
  transition: all 0.12s ease;
  white-space: nowrap;
}

.category-expand-toggle:hover {
  border-color: #0F1117;
  color: #0F1117;
}

[data-bs-theme="dark"] .category-expand-toggle:hover {
  border-color: #38BDF8;
  color: #38BDF8;
}

/* ── Grid & list containers ──────────────────────────────────────────────── */
#grid-view-container .grid {
  --bs-columns: 1;
  display: grid;
  grid-template-columns: repeat(1, 1fr);
  gap: 0.85rem;
}

@media (min-width: 576px) {
  #grid-view-container .grid {
    grid-template-columns: repeat(2, 1fr);
  }
}

@media (min-width: 992px) {
  #grid-view-container .grid {
    grid-template-columns: repeat(3, 1fr);
  }
}

/* ── Description overlay (revealed on card hover) ───────────────────────── */
.resource-desc-overlay {
  font-size: 0.75rem;
  line-height: 1.4;
  color: var(--bs-secondary-color, #6c757d);
  margin-top: 0.3rem;
  margin-bottom: 0.25rem;
  max-height: 0;
  overflow: hidden;
  opacity: 0;
  transition: max-height 0.25s ease, opacity 0.2s ease;
}

.resource-card:hover .resource-desc-overlay,
.resource-card:focus-within .resource-desc-overlay {
  max-height: 6rem;
  opacity: 1;
}

#list-view-container .list-group-item:first-child {
  border-radius: 0.5rem 0.5rem 0 0;
}

#list-view-container .list-group-item:last-child {
  border-radius: 0 0 0.5rem 0.5rem;
}

/* ── Resource date ───────────────────────────────────────────────────────── */
.resource-date {
  font-size: 0.68rem;
  color: var(--bs-secondary-color, #6c757d);
  white-space: nowrap;
  flex-shrink: 0;
}

/* ── Sort select ─────────────────────────────────────────────────────────── */
#sort-select {
  background-color: var(--bs-body-bg);
  border: 1.5px solid var(--bs-border-color, rgba(128, 128, 128, 0.25));
  border-radius: 0.375rem;
  color: var(--bs-body-color);
  font-size: 0.78rem;
  font-weight: 500;
  padding: 0.25rem 1.8rem 0.25rem 0.75rem;
  max-width: 180px;
  cursor: pointer;
}

#sort-select:focus {
  border-color: #38BDF8;
  box-shadow: 0 0 0 3px rgba(56, 189, 248, 0.2);
  outline: none;
}

/* ── No-results message ──────────────────────────────────────────────────── */
#no-results-msg {
  display: none;
  padding: 2.5rem 1rem;
  text-align: center;
  color: var(--bs-secondary-color, #6c757d);
  font-size: 0.9rem;
}

/* ── Pagination ──────────────────────────────────────────────────────────── */
#catalog-pagination {
  margin-top: 1.5rem;
  display: flex;
  justify-content: center;
}

#catalog-pagination .pagination {
  gap: 0.2rem;
  flex-wrap: wrap;
  justify-content: center;
}

#catalog-pagination .page-link {
  font-size: 0.78rem;
  font-weight: 500;
  padding: 0.3rem 0.65rem;
  border-radius: 0.375rem !important;
  border: 1.5px solid var(--bs-border-color, rgba(128, 128, 128, 0.25));
  color: var(--bs-body-color);
  background-color: var(--bs-body-bg);
  transition: all 0.15s ease;
  min-width: 2rem;
  text-align: center;
}

#catalog-pagination .page-link:hover {
  border-color: #38BDF8;
  color: #38BDF8;
  background-color: rgba(56, 189, 248, 0.08);
}

#catalog-pagination .page-item.active .page-link {
  background-color: #38BDF8;
  border-color: #38BDF8;
  color: #0F1117;
}

#catalog-pagination .page-item.disabled .page-link {
  opacity: 0.4;
  cursor: not-allowed;
  pointer-events: none;
}

[data-bs-theme="dark"] #catalog-pagination .page-item.active .page-link {
  background-color: #38BDF8;
  border-color: #38BDF8;
  color: #0F1117;
}
```

```{r setup}
#| message: false
#| warning: false

library(dplyr)
library(stringr)
library(purrr)
library(htmltools)
library(yaml)

# ── Load data from resources.md ───────────────────────────────────────────────
parse_resources_md <- function(path) {
  raw <- readLines(path, encoding = "UTF-8")
  # Split on lines that are exactly "---"
  sep_idx <- which(raw == "---")
  # Each block is between pairs of "---" separators
  # The file format is: --- fields --- --- fields --- ...
  # Blocks start at odd-indexed separators (1,3,5,...) and end at even (2,4,6,...)
  n_seps <- length(sep_idx)
  if (n_seps < 2) return(tibble::tibble())

  records <- vector("list", floor(n_seps / 2))
  for (i in seq_len(floor(n_seps / 2))) {
    start <- sep_idx[2 * i - 1] + 1L
    end   <- sep_idx[2 * i] - 1L
    if (start > end) next
    block_lines <- raw[start:end]
    parsed <- tryCatch(
      yaml::yaml.load(paste(block_lines, collapse = "\n")),
      error = function(e) NULL
    )
    if (!is.null(parsed)) records[[i]] <- parsed
  }

  records <- Filter(Negate(is.null), records)
  dplyr::bind_rows(lapply(records, function(r) {
    tibble::tibble(
      type        = as.character(r$type        %||% ""),
      title       = as.character(r$title       %||% ""),
      link        = as.character(r$link        %||% ""),
      language    = as.character(r$language    %||% ""),
      category    = as.character(r$category    %||% ""),
      description = as.character(r$description %||% ""),
      date        = as.character(r$date        %||% "")
    )
  }))
}

`%||%` <- function(a, b) if (!is.null(a)) a else b

resources_raw <- parse_resources_md(here::here("data", "resources.txt"))

# ── Super-category rules (priority-ordered) ───────────────────────────────────
super_rules <- list(
  "Machine Learning & AI" = c(
    "machine learning", "deep learning", "nlp", "computer vision",
    "neural", "transformer", "gan", "llm", "llms", "diffusion",
    "mlops", "ai", "artificial intelligence", "reinforcement learning",
    "classification", "clustering", "feature engineering"
  ),
  "Statistics" = c(
    "statistics", "bayesian", "bayesian statistics", "mixed model",
    "mixed models", "meta-analysis", "survival", "longitudinal",
    "glmm", "causal", "spc", "regression", "econometrics",
    "time series", "factor analysis", "probability", "inference",
    "frequentist", "sampling", "simulation"
  ),
  "R & Shiny" = c(
    "shiny", "r markdown", "quarto", "renv", "golem", "ggplot2",
    "tidyverse", "web development", "ggplot", "flexdashboard",
    "pkgdown", "renv", "testthat", "devtools", "usethis",
    "programming", "r package", "tidyr", "purrr", "dplyr"
  ),
  "Data Visualization" = c(
    "visualization", "data visualization", "charts", "gallery",
    "color", "dashboard", "dashboards", "plot", "mapping",
    "cartography", "infographic", "d3", "plotly", "leaflet",
    "ggplot2", "highcharts", "vega"
  ),
  "Python & DevOps" = c(
    "python", "docker", "git", "github actions", "deployment",
    "reproducibility", "workflow", "best practices", "devops",
    "kubernetes", "terraform", "ci/cd", "containers",
    "version control", "github", "automation"
  ),
  "Education" = c(
    "tutorial", "course", "education", "guide", "reference",
    "learning", "book", "books", "presentation", "presentations",
    "workshop", "cheatsheet", "exercises"
  ),
  "Community & Events" = c(
    "community", "conference", "forum", "french", "social",
    "newsletter", "blog", "meetup", "podcast"
  ),
  "Life Sciences" = c(
    "pharma", "clinical", "ecology", "bioinformatics", "psychology",
    "genetics", "biomedical", "behavioral", "neuroscience", "health",
    "epidemiology", "genomics", "proteomics"
  ),
  "Research" = c(
    "research", "paper", "preprint", "journal", "academic",
    "arxiv", "publication", "reproducible research", "open science"
  )
)

assign_super <- function(category_str) {
  if (is.na(category_str) || category_str == "") return("General")
  cats <- str_split_1(category_str, ";") |> str_trim() |> tolower()
  for (name in names(super_rules)) {
    if (any(cats %in% super_rules[[name]])) return(name)
  }
  "General"
}

# ── Clean & prepare resources ─────────────────────────────────────────────────
resources <- resources_raw |>
  mutate(
    language = str_replace_all(language, ",\\s*", ";"),
    super = map_chr(category, assign_super)
  ) |>
  arrange(type, title)

n_total <- nrow(resources)
all_types <- sort(unique(resources$type))

# ── Date display helper ───────────────────────────────────────────────────────
# Formats "YYYY-MM-DD" / "YYYY-MM" / "YYYY" → "18 Jan 2024" / "Jan 2024" / "2024"
format_date_display <- function(date_str) {
  if (is.na(date_str) || date_str == "") return("")
  month_names <- c(
    "Jan", "Feb", "Mar", "Apr", "May", "Jun",
    "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"
  )
  parts <- str_split_1(date_str, "-")
  if (length(parts) == 3) {
    day   <- as.integer(parts[3])
    month <- suppressWarnings(as.integer(parts[2]))
    year  <- parts[1]
    if (!is.na(month) && month >= 1 && month <= 12)
      return(paste(day, month_names[month], year))
  } else if (length(parts) == 2) {
    month <- suppressWarnings(as.integer(parts[2]))
    year  <- parts[1]
    if (!is.na(month) && month >= 1 && month <= 12)
      return(paste(month_names[month], year))
  }
  date_str  # fallback: return as-is (e.g. "2024")
}

# ── Type badge color mapping ──────────────────────────────────────────────────
type_color <- function(type) {
  switch(type,
    "Package" = , "Tool" = , "App" = , "Platform" = , "Repository" = "primary",
    "Course" = , "Tutorial" = , "Guide" = , "Workshop" = "success",
    "Book" = , "Documentation" = , "Paper" = , "Journal" = ,
    "Magazine" = , "Slides" = "info",
    "Blog" = , "Website" = , "Video" = , "Gallery" = "warning",
    "Community" = , "Forum" = , "Conference" = , "Social" = ,
    "Newsletter" = "secondary",
    "dark"
  )
}

# ── Language chip helper ──────────────────────────────────────────────────────
lang_chip <- function(lang_str) {
  if (is.na(lang_str) || lang_str == "") return(NULL)
  parts <- str_split_1(lang_str, ";") |> str_trim()
  map(parts, function(l) {
    cls <- switch(tolower(l),
      r = "chip chip-r",
      python = "chip chip-python",
      julia = "chip chip-julia",
      "chip chip-other"
    )
    tags$span(class = cls, l)
  })
}

# ── Category chips helper (max visible + expand toggle) ───────────────────────
cat_chips <- function(cat_str, uid, max_shown = 3L) {
  if (is.na(cat_str) || cat_str == "") return(NULL)
  parts <- str_split_1(cat_str, ";") |> str_trim()
  n <- length(parts)
  shown <- parts[seq_len(min(max_shown, n))]
  extra <- if (n > max_shown) parts[(max_shown + 1L):n] else character(0L)
  extra_id <- paste0("extra-", uid)

  visible_chips <- map(shown, function(c) tags$span(class = "chip chip-cat", c))

  if (length(extra) == 0L) {
    return(visible_chips)
  }

  extra_chips <- map(extra, function(c) {
    tags$span(
      class = "chip chip-cat d-none",
      `data-extra` = extra_id,
      c
    )
  })

  expand_btn <- tags$button(
    class = "category-expand-toggle",
    `data-id` = extra_id,
    paste0("+", length(extra))
  )

  list(visible_chips, extra_chips, expand_btn)
}

# ── Build one card + one list item ────────────────────────────────────────────
make_resource <- function(i) {
  row <- resources[i, ]
  type <- row$type
  title_text <- row$title
  link <- row$link
  lang_str <- row$language
  cat_str <- row$category
  super <- row$super
  desc <- row$description
  date_raw <- row$date
  date_display <- format_date_display(date_raw)

  # Filtering attributes (all lowercase for simple JS string matching)
  data_attrs <- list(
    `data-type` = tolower(type),
    `data-language` = tolower(lang_str),
    `data-categories` = tolower(cat_str),
    `data-super` = tolower(super),
    `data-description` = tolower(desc),
    `data-date` = date_raw  # ISO format for JS sort (YYYY-MM-DD / YYYY-MM / YYYY)
  )

  lchips <- lang_chip(lang_str)
  cchips <- cat_chips(cat_str, i)
  badge <- tags$span(
    class = paste0("badge resource-type bg-", type_color(type)),
    type
  )
  title_link <- tags$a(
    href = link,
    target = "_blank",
    rel = "noopener noreferrer",
    title = if (nchar(desc) > 0) desc else NULL,
    title_text
  )

  # Description overlay (hidden by default, revealed on card hover)
  desc_el <- if (nchar(desc) > 0) {
    tags$div(
      class = "resource-desc-overlay",
      desc
    )
  } else NULL

  # Date element (shown when available)
  date_el <- if (nchar(date_display) > 0) {
    tags$span(class = "resource-date", date_display)
  } else NULL

  # ── Grid card ──────────────────────────────────────────────────────────────
  grid_item <- do.call(tags$div, c(
    list(class = "g-col"),
    data_attrs,
    list(
      tags$div(
        class = "card resource-card h-100",
        tags$div(
          class = "card-body",
          tags$div(
            class = "d-flex justify-content-between align-items-start mb-2",
            badge,
            tags$div(class = "d-flex flex-wrap gap-1 justify-content-end", lchips)
          ),
          tags$div(
            class = "d-flex justify-content-between align-items-baseline gap-2 mb-1",
            tags$div(class = "resource-title", title_link),
            date_el
          ),
          desc_el,
          tags$div(
            class = "cat-chips",
            style = "line-height: 1.9;",
            cchips
          )
        )
      )
    )
  ))

  # ── List item ──────────────────────────────────────────────────────────────
  list_item <- do.call(tags$li, c(
    list(class = "list-group-item resource-item"),
    data_attrs,
    list(
      tags$div(
        class = "d-flex align-items-center gap-2 flex-wrap",
        badge,
        tags$span(class = "resource-title flex-grow-1", title_link),
        tags$div(class = "d-flex gap-1 flex-wrap flex-shrink-0", lchips),
        date_el
      ),
      tags$div(
        class = "cat-chips mt-1",
        style = "line-height: 1.9;",
        cchips
      )
    )
  ))

  list(grid = grid_item, list = list_item)
}

# ── Render all resources ──────────────────────────────────────────────────────
all_resources <- map(seq_len(nrow(resources)), make_resource)
grid_items <- map(all_resources, "grid")
list_items <- map(all_resources, "list")
```

```{r controls}
# ── Build controls HTML ───────────────────────────────────────────────────────

# Language filter chips
lang_chip_defs <- list(
  list(value = "r",      label = "R",      color = "color: #1a579d; border-color: rgba(26,87,157,0.4);"),
  list(value = "python", label = "Python", color = "color: #3a7a20; border-color: rgba(55,125,34,0.4);"),
  list(value = "julia",  label = "Julia",  color = "color: #8b33b3; border-color: rgba(149,57,191,0.4);"),
  list(value = "other",  label = "Other",  color = "color: #555f6a; border-color: rgba(108,117,125,0.35);")
)

# Super-category filter chips
super_chip_defs <- list(
  list(value = "machine learning & ai", label = "ML & AI"),
  list(value = "statistics",            label = "Statistics"),
  list(value = "r & shiny",             label = "R & Shiny"),
  list(value = "data visualization",    label = "Viz"),
  list(value = "python & devops",       label = "Python & DevOps"),
  list(value = "education",             label = "Education"),
  list(value = "community & events",    label = "Community"),
  list(value = "life sciences",         label = "Life Sciences"),
  list(value = "research",              label = "Research"),
  list(value = "general",              label = "General")
)

make_chip <- function(value, label, extra_style = NULL) {
  attrs <- list(
    class = "btn filter-chip",
    `data-filter-group` = if (value %in% map_chr(lang_chip_defs, "value")) "language" else "super",
    `data-filter-value` = value,
    `aria-pressed` = "false"
  )
  if (!is.null(extra_style)) attrs$style <- extra_style
  do.call(tags$button, c(attrs, list(label)))
}

lang_chips_html <- map(lang_chip_defs, function(d) {
  make_chip(d$value, d$label, d$color)
})

super_chips_html <- map(super_chip_defs, function(d) {
  attrs <- list(
    class = "btn filter-chip",
    `data-filter-group` = "super",
    `data-filter-value` = d$value,
    `aria-pressed` = "false"
  )
  do.call(tags$button, c(attrs, list(d$label)))
})

type_options <- c(
  list(tags$option(value = "", "All types")),
  map(all_types, function(t) tags$option(value = tolower(t), t))
)

tagList(
  tags$div(
    class = "controls-wrapper",
    # Row 1: search + view toggle
    tags$div(
      class = "controls-search-row",
      tags$div(
        class = "resource-search-wrap input-group",
        tags$span(
          class = "input-group-text",
          tags$i(class = "bi bi-search")
        ),
        tags$input(
          type = "text",
          id = "resource-search",
          class = "form-control",
          placeholder = paste0("Search ", n_total, " resources by title or category\u2026"),
          `aria-label` = "Search resources"
        )
      ),
      # View toggle
      tags$div(
        class = "d-flex gap-1 flex-shrink-0",
        tags$input(
          type = "radio",
          class = "btn-check",
          name = "view-toggle",
          id = "grid-view-btn",
          checked = NA
        ),
        tags$label(
          class = "view-toggle-label",
          `for` = "grid-view-btn",
          tags$i(class = "bi bi-grid-3x3-gap me-1"),
          "Grid"
        ),
        tags$input(
          type = "radio",
          class = "btn-check",
          name = "view-toggle",
          id = "list-view-btn"
        ),
        tags$label(
          class = "view-toggle-label",
          `for` = "list-view-btn",
          tags$i(class = "bi bi-list-ul me-1"),
          "List"
        )
      )
    ),
    # Row 2: language chips
    tags$div(
      class = "controls-chips-row",
      tags$span(class = "filter-section-label", "Language"),
      tags$div(class = "filter-divider"),
      lang_chips_html
    ),
    # Row 3: super-category chips
    tags$div(
      class = "controls-chips-row",
      tags$span(class = "filter-section-label", "Topic"),
      tags$div(class = "filter-divider"),
      super_chips_html
    ),
    # Row 4: type dropdown + sort + clear + counter
    tags$div(
      class = "controls-bottom-row",
      do.call(tags$select, c(list(id = "type-filter"), type_options)),
      tags$select(
        id = "sort-select",
        tags$option(value = "default", "Sort: A \u2192 Z"),
        tags$option(value = "date-desc", "Sort: Date \u2193 (newest)"),
        tags$option(value = "date-asc",  "Sort: Date \u2191 (oldest)")
      ),
      tags$button(
        id = "clear-filters",
        class = "btn btn-sm",
        style = "font-size: 0.78rem; border: 1.5px solid var(--bs-border-color, rgba(128,128,128,0.25)); border-radius: 0.375rem; padding: 0.25rem 0.65rem;",
        tags$i(class = "bi bi-x-circle me-1"),
        "Clear"
      ),
      tags$div(
        class = "catalog-counter",
        "Showing ",
        tags$strong(id = "resources-count", as.character(n_total)),
        " of ",
        tags$strong(as.character(n_total)),
        " resources"
      )
    )
  )
)
```

```{r cards}
# ── Grid + List views ─────────────────────────────────────────────────────────
tagList(
  # Grid view
  tags$div(
    id = "grid-view-container",
    tags$div(
      class = "grid",
      grid_items
    )
  ),
  # List view (hidden by default)
  tags$div(
    id = "list-view-container",
    class = "d-none",
    tags$ul(
      class = "list-group",
      list_items
    )
  ),
  # No results message
  tags$div(
    id = "no-results-msg",
    tags$i(class = "bi bi-search me-2"),
    "No resources match your current filters.",
    tags$button(
      id = "no-results-clear",
      class = "btn btn-link btn-sm p-0 ms-2",
      style = "font-size: inherit;",
      "Clear filters"
    )
  ),
  # Pagination nav
  tags$div(id = "catalog-pagination")
)
```

```{=html}
<script>
document.addEventListener('DOMContentLoaded', function () {
  // ── Cache DOM elements ────────────────────────────────────────────────────
  const searchInput     = document.getElementById('resource-search');
  const typeSelect      = document.getElementById('type-filter');
  const clearBtn        = document.getElementById('clear-filters');
  const noResultsClear  = document.getElementById('no-results-clear');
  const noResultsMsg    = document.getElementById('no-results-msg');
  const gridContainer   = document.getElementById('grid-view-container');
  const listContainer   = document.getElementById('list-view-container');
  const gridViewBtn     = document.getElementById('grid-view-btn');
  const listViewBtn     = document.getElementById('list-view-btn');
  const countEl         = document.getElementById('resources-count');
  const paginationEl    = document.getElementById('catalog-pagination');
  const sortSelect      = document.getElementById('sort-select');

  if (!searchInput || !gridContainer || !listContainer) return;

  // ── Pagination state ──────────────────────────────────────────────────────
  const PAGE_SIZE = 50;
  let currentPage = 1;
  let visibleWrappers = []; // ordered list of wrappers passing current filters

  // ── Active filter state ───────────────────────────────────────────────────
  const activeFilters = { language: new Set(), super: new Set() };

  // ── Helpers ───────────────────────────────────────────────────────────────
  function getGridWrappers() {
    return Array.from(gridContainer.querySelectorAll('.g-col'));
  }
  function getListWrappers() {
    return Array.from(listContainer.querySelectorAll('.list-group-item'));
  }

  // ── Core filter logic — builds visibleWrappers, then renders page 1 ───────
  function applyAll(resetPage) {
    if (resetPage === undefined) resetPage = true;
    const query    = searchInput.value.trim().toLowerCase();
    const typeVal  = typeSelect.value.toLowerCase();
    const langSet  = activeFilters.language;
    const superSet = activeFilters.super;

    const gridWrappers = getGridWrappers();
    const listWrappers = getListWrappers();

    visibleWrappers = [];

    gridWrappers.forEach(function (wrapper, idx) {
      const listWrap = listWrappers[idx];
      let show = true;

      // Search
      if (show && query) {
        const titleEl  = wrapper.querySelector('.resource-title a');
        const title    = titleEl ? titleEl.textContent.toLowerCase() : '';
        const cats     = (wrapper.dataset.categories || '').toLowerCase();
        const descText = (wrapper.dataset.description || '').toLowerCase();
        show = title.includes(query) || cats.includes(query) || descText.includes(query);
      }

      // Type dropdown
      if (show && typeVal) {
        show = (wrapper.dataset.type || '') === typeVal;
      }

      // Language chips (OR)
      if (show && langSet.size > 0) {
        const langs = (wrapper.dataset.language || '').split(';').map(function (s) {
          return s.trim().toLowerCase();
        });
        show = Array.from(langSet).some(function (f) { return langs.includes(f); });
      }

      // Super-category chips (OR)
      if (show && superSet.size > 0) {
        const sup = (wrapper.dataset.super || '').toLowerCase();
        show = superSet.has(sup);
      }

      // Hide everything for now; renderPage will reveal the current slice
      wrapper.style.display = 'none';
      if (listWrap) listWrap.style.display = 'none';

      if (show) visibleWrappers.push(idx);
    });

    // Sort visible indices
    const sortMode = sortSelect ? sortSelect.value : 'default';
    sortVisibleWrappers(sortMode, getGridWrappers());

    // Update counter
    if (countEl) countEl.textContent = visibleWrappers.length;

    // Show/hide no-results message
    if (noResultsMsg) {
      noResultsMsg.style.display = visibleWrappers.length === 0 ? 'block' : 'none';
    }

    if (resetPage) currentPage = 1;
    renderPage(currentPage);
  }

  // ── Sort visibleWrappers in place ─────────────────────────────────────────
  function sortVisibleWrappers(mode, gridWrappers) {
    if (mode === 'default') return; // preserve DOM order (R sort: type + title)

    visibleWrappers.sort(function (a, b) {
      const dateA = (gridWrappers[a] && gridWrappers[a].dataset.date) || '';
      const dateB = (gridWrappers[b] && gridWrappers[b].dataset.date) || '';

      // Items without a date always go last
      if (!dateA && !dateB) return 0;
      if (!dateA) return 1;
      if (!dateB) return -1;

      if (mode === 'date-desc') return dateA < dateB ? 1 : dateA > dateB ? -1 : 0;
      if (mode === 'date-asc')  return dateA > dateB ? 1 : dateA < dateB ? -1 : 0;
      return 0;
    });
  }

  // ── Render a page slice ───────────────────────────────────────────────────
  function renderPage(page) {
    const gridWrappers = getGridWrappers();
    const listWrappers = getListWrappers();
    const totalPages   = Math.ceil(visibleWrappers.length / PAGE_SIZE);

    // Clamp page
    if (page < 1) page = 1;
    if (page > totalPages && totalPages > 0) page = totalPages;
    currentPage = page;

    const start = (page - 1) * PAGE_SIZE;
    const end   = start + PAGE_SIZE;
    const pageSlice = new Set(visibleWrappers.slice(start, end));

    gridWrappers.forEach(function (wrapper, idx) {
      const listWrap = listWrappers[idx];
      const show = pageSlice.has(idx);
      wrapper.style.display = show ? '' : 'none';
      if (listWrap) listWrap.style.display = show ? '' : 'none';
    });

    renderPagination(visibleWrappers.length, currentPage);
  }

  // ── Render pagination nav ─────────────────────────────────────────────────
  function renderPagination(total, page) {
    if (!paginationEl) return;
    const totalPages = Math.ceil(total / PAGE_SIZE);

    if (totalPages <= 1) {
      paginationEl.innerHTML = '';
      return;
    }

    const nav  = document.createElement('nav');
    nav.setAttribute('aria-label', 'Resources pagination');
    const ul = document.createElement('ul');
    ul.className = 'pagination';

    // Helper: make a page-item
    function makeItem(label, targetPage, isActive, isDisabled, ariaLabel) {
      const li = document.createElement('li');
      li.className = 'page-item' +
        (isActive   ? ' active'   : '') +
        (isDisabled ? ' disabled' : '');
      const a = document.createElement('a');
      a.className = 'page-link';
      a.href = '#';
      a.innerHTML = label;
      if (ariaLabel) a.setAttribute('aria-label', ariaLabel);
      if (isActive) a.setAttribute('aria-current', 'page');
      if (!isDisabled && !isActive) {
        a.addEventListener('click', function (e) {
          e.preventDefault();
          renderPage(targetPage);
          // Scroll to top of controls
          const ctrl = document.querySelector('.controls-wrapper');
          if (ctrl) ctrl.scrollIntoView({ behavior: 'smooth', block: 'start' });
        });
      } else {
        a.addEventListener('click', function (e) { e.preventDefault(); });
      }
      li.appendChild(a);
      return li;
    }

    // Prev
    ul.appendChild(makeItem('&laquo;', page - 1, false, page === 1, 'Previous page'));

    // Page numbers — show a window around the current page
    const WINDOW = 2;
    let rangeStart = Math.max(1, page - WINDOW);
    let rangeEnd   = Math.min(totalPages, page + WINDOW);

    // Always show first page
    if (rangeStart > 1) {
      ul.appendChild(makeItem('1', 1, false, false));
      if (rangeStart > 2) {
        const li = document.createElement('li');
        li.className = 'page-item disabled';
        li.innerHTML = '<span class="page-link">&hellip;</span>';
        ul.appendChild(li);
      }
    }

    for (var p = rangeStart; p <= rangeEnd; p++) {
      ul.appendChild(makeItem(String(p), p, p === page, false));
    }

    // Always show last page
    if (rangeEnd < totalPages) {
      if (rangeEnd < totalPages - 1) {
        const li = document.createElement('li');
        li.className = 'page-item disabled';
        li.innerHTML = '<span class="page-link">&hellip;</span>';
        ul.appendChild(li);
      }
      ul.appendChild(makeItem(String(totalPages), totalPages, false, false));
    }

    // Next
    ul.appendChild(makeItem('&raquo;', page + 1, false, page === totalPages, 'Next page'));

    nav.appendChild(ul);
    paginationEl.innerHTML = '';
    paginationEl.appendChild(nav);
  }

  // ── Search (debounced) ────────────────────────────────────────────────────
  function debounce(fn, ms) {
    var t;
    return function () { clearTimeout(t); t = setTimeout(fn, ms); };
  }

  searchInput.addEventListener('input', debounce(function () { applyAll(true); }, 280));

  // ── Type dropdown ─────────────────────────────────────────────────────────
  typeSelect.addEventListener('change', function () { applyAll(true); });

  // ── Sort dropdown ─────────────────────────────────────────────────────────
  if (sortSelect) sortSelect.addEventListener('change', function () { applyAll(true); });

  // ── Filter chips (event delegation) ──────────────────────────────────────
  document.addEventListener('click', function (e) {
    var chip = e.target.closest('.filter-chip');
    if (!chip) return;
    var group = chip.dataset.filterGroup;
    var value = chip.dataset.filterValue;
    if (!group || !value) return;

    if (chip.classList.contains('active')) {
      chip.classList.remove('active');
      chip.setAttribute('aria-pressed', 'false');
      activeFilters[group].delete(value);
    } else {
      chip.classList.add('active');
      chip.setAttribute('aria-pressed', 'true');
      activeFilters[group].add(value);
    }
    applyAll(true);
  });

  // ── Clear all filters ─────────────────────────────────────────────────────
  function clearAll() {
    searchInput.value = '';
    typeSelect.value  = '';
    if (sortSelect) sortSelect.value = 'default';
    activeFilters.language.clear();
    activeFilters.super.clear();
    document.querySelectorAll('.filter-chip.active').forEach(function (c) {
      c.classList.remove('active');
      c.setAttribute('aria-pressed', 'false');
    });
    applyAll(true);
  }

  clearBtn.addEventListener('click', clearAll);
  if (noResultsClear) noResultsClear.addEventListener('click', clearAll);

  // ── View toggle ───────────────────────────────────────────────────────────
  if (gridViewBtn) {
    gridViewBtn.addEventListener('change', function () {
      if (this.checked) {
        gridContainer.classList.remove('d-none');
        listContainer.classList.add('d-none');
      }
    });
  }
  if (listViewBtn) {
    listViewBtn.addEventListener('change', function () {
      if (this.checked) {
        listContainer.classList.remove('d-none');
        gridContainer.classList.add('d-none');
      }
    });
  }

  // ── Category expand toggle (event delegation) ─────────────────────────────
  document.body.addEventListener('click', function (e) {
    var btn = e.target.closest('.category-expand-toggle');
    if (!btn) return;
    e.stopPropagation();
    var targetId = btn.getAttribute('data-id');
    var extras   = document.querySelectorAll('[data-extra="' + targetId + '"]');
    extras.forEach(function (badge) { badge.classList.remove('d-none'); });
    btn.style.display = 'none';
  });

  // Initial render
  applyAll(true);
});
</script>
```

::: {.callout-note}
## Contributing
Want to add a resource? Edit `data/resources.txt` and open a PR on [GitHub](https://github.com/antoinelucasfra/antoinelucasfra.github.io). Each resource is a small YAML block:

```yaml
---
title: "Resource Title"
type: Book
link: https://example.com
language: R
category: "Statistics;Tutorial"
description: "A brief one-sentence description shown on hover and in search."
---
```

The `description` field is optional but recommended — it powers the hover tooltip on each card title and is included in the full-text search.

See [CONTRIBUTING.md](https://github.com/antoinelucasfra/antoinelucasfra.github.io/blob/main/CONTRIBUTING.md) for the full guide, including the automated workflow for adding resources via Google Keep.
:::

*Links to external websites are provided for convenience and informational purposes only.*
