---
title: "Resources Catalog"
subtitle: "A curated collection of data science resources for R, Python, and beyond."
description: "A curated and filterable catalog of 1,000+ data science resources for R, Python, and beyond."
search: false
format:
  html:
    toc: false
    page-layout: full
    css: ../assets/stylesheets/resources-catalog.css
execute:
  echo: false
---

## Overview

This project turns a plain-text resource list into a searchable front end for curated data science references across R, Python, statistics, visualization, research workflows, and life sciences.

It is intentionally both a curation project and a small product-engineering exercise: define a lightweight schema, keep the source easy to edit, and ship a fast browsing experience without introducing a heavyweight backend.

## What This Project Includes

- A hand-curated catalog stored in `data/resources.txt`, with each entry typed, categorized, and optionally annotated with a short description
- A Quarto + R generation layer that builds the filter controls, cards, counters, and pagination from a single source of truth
- Lightweight client-side search and filtering for language, topic, type, layout, and sort order
- A low-friction contribution workflow based on small YAML blocks and documented pull requests

```{r resource-catalog-setup}
#| message: false
#| warning: false

library(dplyr)
library(htmltools)
library(purrr)
library(stringr)
library(yaml)

source(here::here("_helpers", "resources_catalog.R"))

resources <- load_resources_catalog(here::here("data", "resources.txt"))

n_total <- nrow(resources)
all_types <- sort(unique(resources$type))
cards <- map(seq_len(n_total), function(index) {
  make_resource_card(resources[index, ], index)
})
```

```{r resource-catalog-controls}
# ── Build chip filters ──────────────────────────────────────────────────

make_chip <- function(value, label, group, extra_style = NULL) {
  attrs <- list(
    class = "btn filter-chip",
    `data-filter-group` = group,
    `data-filter-value` = value,
    `aria-pressed` = "false"
  )
  if (!is.null(extra_style)) attrs$style <- extra_style
  do.call(tags$button, c(attrs, list(label)))
}

lang_chips_html <- imap(LANG_CHIP_STYLES, function(style, lang) {
  make_chip(lang, stringr::str_to_title(lang), "language", style)
})

super_chips_html <- imap(SUPER_CHIP_LABELS, function(label, value) {
  make_chip(value, label, "super")
})

type_options <- c(
  list(tags$option(value = "", "All types")),
  map(all_types, function(t) tags$option(value = tolower(t), t))
)

tagList(
  tags$div(
    class = "controls-wrapper",
    # Search
    tags$div(
      class = "resource-search-wrap input-group",
      tags$span(class = "input-group-text", tags$i(class = "bi bi-search")),
      tags$input(
        type = "text", id = "resource-search", class = "form-control",
        placeholder = paste0("Search ", n_total, " resources\u2026"),
        `aria-label` = "Search resources"
      )
    ),
    # Language chips
    tags$div(class = "controls-chips-row",
      tags$span(class = "filter-section-label", "Language"),
      tags$div(class = "filter-divider"),
      lang_chips_html
    ),
    # Super-category chips
    tags$div(class = "controls-chips-row",
      tags$span(class = "filter-section-label", "Topic"),
      tags$div(class = "filter-divider"),
      super_chips_html
    ),
    # Type dropdown + sort + clear + counter
    tags$div(class = "controls-bottom-row",
      do.call(tags$select, c(list(id = "type-filter"), type_options)),
      tags$select(id = "sort-select",
        tags$option(value = "default", "Sort: A \u2192 Z"),
        tags$option(value = "date-desc", "Sort: Date \u2193 (newest)"),
        tags$option(value = "date-asc",  "Sort: Date \u2191 (oldest)")
      ),
      tags$button(id = "clear-filters", class = "btn btn-sm",
        style = "font-size: 0.78rem; border: 1.5px solid var(--bs-border-color, rgba(128,128,128,0.25)); border-radius: 0.375rem; padding: 0.25rem 0.65rem;",
        tags$i(class = "bi bi-x-circle me-1"), "Clear"),
      tags$div(class = "catalog-counter",
        "Showing ", tags$strong(id = "resources-count", as.character(n_total)),
        " of ", tags$strong(as.character(n_total)), " resources"
      )
    )
  )
)
```

```{r resource-catalog-cards}
# ── Results view ────────────────────────────────────────────────────────
tagList(
  tags$div(id = "resource-catalog", class = "catalog-view",
    tags$div(id = "catalog-results", class = "catalog-results", cards),
    tags$div(id = "no-results-msg",
      tags$i(class = "bi bi-search me-2"),
      "No resources match your current filters.",
      tags$button(id = "no-results-clear", class = "btn btn-link btn-sm p-0 ms-2",
        style = "font-size: inherit;", "Clear filters")
    )
  ),
  tags$div(id = "catalog-pagination")
)
```

```{=html}
<script src="../assets/scripts/resources-catalog.js"></script>
```

:::: {.callout-note}
## Contributing
Want to add a resource? Edit `data/resources.txt` and open a PR on [GitHub](https://github.com/antoinelucasfra/antoinelucasfra.github.io). Each resource is a small YAML block:

```yaml
---
title: "Resource Title"
type: Book
link: https://example.com
language: R
category: "Statistics;Tutorial"
description: "A brief one-sentence description shown on hover and in search."
---
```

The `description` field is optional but recommended — it powers the hover tooltip on each card title and is included in the full-text search.

See [CONTRIBUTING.md](https://github.com/antoinelucasfra/antoinelucasfra.github.io/blob/main/CONTRIBUTING.md) for the full guide, including the automated workflow for adding resources via Google Keep.
::::

*Links to external websites are provided for convenience and informational purposes only.*
